---
title: "VarSleuth"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VarSleuth

<!-- badges: start -->
<!-- badges: end -->

VarSleuth is an open-source R package for interpreting genetic variants according to the ACMG guidelines. 

## Installation

You can install VarSleuth directly from GitHub with:

```r
# If you haven't installed 'devtools' yet, do so first
if (!require(devtools)) {
  install.packages("devtools")
}

# Install VarSleuth from GitHub
devtools::install_github("ronaldosfjunior/VarSleuth")

## Example
```

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VarSleuth)
## basic example code
# UNDER CONSTRUCTION
```

# Contributing

We welcome contributions from the community! If you'd like to contribute, please fork the repository and submit a pull request.

# License

VarSleuth is open source software released under the MIT license. See the LICENSE file for more details.
